Differential Expression - MSSM-Penn-Pitt - ACC - Dx_Sex

### 2020-07-29 individual-cohorts/MSSM-Penn-Pitt_ACC_DE.Rmd
typo

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn22012953';
activityName = 'Differential Expression';
activityDescription = 'Differential Expression - Dx - Sex';

@@

contrast <- c(glue::glue_collapse(names(L1[L1 != 0]), "-"), 
              glue::glue_collapse(names(L2[L2 != 0]), "-"),
              glue::glue_collapse(names(L3[L3 != 0]), "-"),
              glue::glue("Dx_SexControl_Female-Dx_SexOther_FemaleDx_SexSCZ_Female"),
              glue::glue("Dx_SexControl_Male-Dx_SexOther_MaleDx_SexSCZ_Male"),

)

>>>>

```{r synapse.parameters, include=FALSE, cache=FALSE}
parentId = 'syn22012953';
activityName = 'Differential Expression';
activityDescription = 'Differential Expression - Dx - Sex';

@@

contrast <- c(glue::glue_collapse(names(L1[L1 != 0]), "-"), 
              glue::glue_collapse(names(L2[L2 != 0]), "-"),
              glue::glue_collapse(names(L3[L3 != 0]), "-"),
              glue::glue("Dx_SexControl_Female-Dx_SexOther_FemaleDx_SexSCZ_Female"),
              glue::glue("Dx_SexControl_Male-Dx_SexOther_MaleDx_SexSCZ_Male")
)
